Topological Equivariant Artist Model for Visualization Library Architecture

### 2023-10-13 paper/main.tex
intro + ref

 In this paper, we propose a methodology for describing structure, verifying structure preservation, and specifying the conditions for constructing a structure preserving map between data and graphics using topology and category theory.

 We use category theory because it is the math of structures and their relations and therefore provides a robust framework for defining structure and expressing the conditions under which structure would be preserved.

 We encode the structure of the data and graphics in a uniform generalizable manner ; doing so allows us to discuss everything from lines to complex ND spaces with the same interface.

>>>>

In this paper, we propose a methodology for describing structure, verifying structure preservation, and specifying the conditions for constructing a structure preserving map between data and graphics using topology and category theory. We use category theory because it is the math of structures and their relations and therefore provides a robust framework for defining structure and expressing the conditions under which structure would be preserved. We encode the structure of the data and graphics in a uniform generalizable manner; doing so allows us to use the same framework for describing, for example, how tables and scatter plots and heatmaps 
are different views of the same underlying data or the ways in which a time series and map drawn from the same data cube are linked.
